State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
its just a check

%<-comment out this for checking equations (author list too)
% \usepackage{iopams,setstack} 
%<-comment out this for checking equations
\usepackage{graphicx}
\usepackage{algorithm, algorithmicx, algpseudocode} 
\usepackage{color} 
\usepackage[tight,scriptsize]{subfigure}
% \usepackage{pstool}
\renewcommand{\subcapsize}{\small}
 \usepackage{anysize}							%<-use this for checking equation length
 % \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
%  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
 \usepackage{amsmath}
\usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} \begin{document}

@@

The sensors were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm. This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings. Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{SpectralAnalysisSection} given access to the true field. \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).} 
  \begin{figure}\label{fig:experimental design}
  	\begin{center}
  		\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePy_1.pdf} 
  	\end{center}
  	\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis}
  \end{figure}

\begin{figure}[th]
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/zeta.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0.pdf}}\\
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta1.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2.pdf}}\\
\caption{Distribution of the parameters estimates over 272
runs.}
\label{fig:Parameters}
\end{figure}
\subsection{Spatial Frequency Analysis} In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{} shows the spatial frequency of the field. The cut-off frequency, $\nu_c$, was taken to be \omg{??}, which corresponds to the \omg{??-3~dB} from the peak power. From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \omg{??}. This confirms our separation was enough to prevent problems associated with aliasing.

>>>>

%<-comment out this for checking equations (author list too)
% \usepackage{iopams,setstack} 
%<-comment out this for checking equations
\usepackage{graphicx}
\usepackage{algorithm, algorithmicx, algpseudocode} 
\usepackage{color} 
%This is to decrease the space in subfigure command
\usepackage[tight,scriptsize]{subfigure}
\makeatletter
\renewcommand{\subfigtopskip}{1\p@}
\renewcommand{\subfigcapskip}{0\p@}
\renewcommand{\subfigcaptopadj}{1\p@}
\renewcommand{\subfigbottomskip}{1\p@}
\renewcommand{\subfiglabelskip}{0.05em plus 0.02em minus 0.01em}
\makeatother
% \usepackage{pstool}
\renewcommand{\subcapsize}{\small}
 \usepackage{anysize}							%<-use this for checking equation length
 % \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
%  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
 \usepackage{amsmath}
\usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} \begin{document}

@@

The sensors were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm. This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings. Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{SpectralAnalysisSection} given access to the true field. \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).} 
   \begin{figure}\label{fig:experimental design}
   	\begin{center}
   		\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePy_1.pdf} 
   	\end{center}
   	\caption{Example of experimental design and model output. \textbf{a}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{b} Example of data generated by the model through the observations. \textbf{c}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} 
   \end{figure}
% \begin{figure}[th]\label{fig:experimental design}
% \begin{center}
% \subfigure[][]{\includegraphics[width=0.35\textwidth]{./Graph/ExperimentFigurePy.pdf}}\\
% \subfigure[][]{\includegraphics[width=0.35\textwidth]{./Graph/ExperimentFigureEEGPy.pdf}}\\
% \subfigure[][]{\includegraphics[width=0.35\textwidth]{./Graph/ExperimentFigurePSDPy.pdf}}
% \end{center}
% \caption{Example of experimental design and model output. \textbf{a}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{b} Example of data generated by the model through the observations. \textbf{c}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} 
% \end{figure}
\begin{figure}[th]
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/zeta.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0.pdf}}\\
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta1.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2.pdf}}
\caption{Distribution of the parameters estimates over 272
runs.}
\label{fig:Parameters}
\end{figure}
\subsection{Spatial Frequency Analysis} In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{} shows the spatial frequency of the field. The cut-off frequency, $\nu_c$, was taken to be \omg{??}, which corresponds to the \omg{??-3~dB} from the peak power. From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \omg{??}. This confirms our separation was enough to prevent problems associated with aliasing.
